Attack-Tolerant Networks: A Structural, Multipath Approach

### 2016-08-04 wsdm-2017/source/paper.tex
Finish revisions to introduction.

In addition we provide a novel concurrent multipath routing algorithm
on the butterfly network topology and use the partial trust model to prove
a high level of adversarial fault tolerance.
While the ability to control network topology is only achievable in some
applications, those applications are nonetheless significant,
e.g. overlay networks \cite{lua_survey_2005, korzun_structured_2013},
formal organizations \cite{mohr_explaining_1982},
government-regulated cellular networks \cite{walker_mass_2012},
and call tree notification systems \cite{nickerson_thinking_2010}.

@@

Given the above framework, we develop and evaluate a \emph{multipath routing} technique to reduce 
the likelihood that compromised nodes are undetected during the information 
routing process by allowing multiple copies of a message to be sent through independent paths,
which can be used for error-detection and error-correction by the receiver.

The multipath routing technique relies on the existence and discoverability of
multiple redundant paths between the source and the destination. Thus, network 
structure and routing algorithms play a key role in the success of the technique.
We formally evaluate the 
effects of network structure on attack-resistance and show that the probability
of undetected 
errors decreases exponentially with the number of independent paths between 
source and destination.

The mutlipath routing technique is well-suted for {\em structured networks},
in which links between nodes are constrained to a particular architecture.
Specifically, we employ the butterfly network topology,
used elsewhere in parallel computing \cite{kshemkalyani_distributed_2008}
and peer-to-peer \cite{lua_survey_2005, korzun_structured_2013}
applications.
For this network topology,
we propose an efficient, attack-tolerant multipath routing algorithm.

Our main contributions are:
\begin{itemize}
\item{We develop a decentralized {\em partial trust model},
which makes weaker transitivity assumptions than previous web-of-trust models,
and use this model to quantify the effects of network structure on
fault tolerance;}
\item{We show that as the number of disjoint paths between the neighborhoods
of the sender and reciever grows,
the probability of successfully detecting adversarial faults
approaches 1 exponentially.
Furthermore, we show that the number of disjoint paths is a function of
network structure;}
\item{We present a scalable, efficient, and attack-tolerant multipath
routing algorithm on the butterfly network topology.}
\end{itemize}

This paper is organized as follows.
Section 2. reviews background and related work.
Section 3. discusses the desired properties of attack-tolerant network
infrastructure.
Section 4. proposes the partial trust model.
Section 5. proposes a general technique for multipath fault tolerance on
structured networks.
Section 6. proposes a specific application of this technique to the butterfly
network topology.
Section 7. discusses these results.
And Section 8. concludes.

>>>>

@@

Using the partial trust model, we are able to reduce complex networks to
simply a number of redundant, independent paths.
This reduction enables the application of standard error detection techniques,
which rely on statistically independent errors.
While adversarial faults along a single path are correlated,
faults in randomly-chosen independent paths are not.
Thus fault tolerance techniques can be applied,
even in the presence of adversarial errors,
when messages are sent in parallel,
a technique known as {\em concurrent multipath routing}
\cite{zin_survey_2015, qadir_exploiting_2015}.
The receiver can then use the redundant messages to detect and/or correct
errors.
Using the partial trust model, we formally evaluate the 
effects of network structure on attack-resistance and show that the probability
of undetected errors decreases exponentially with the number of
independent paths between source and destination,
even when no individual path is entirely trusted.

Our specific multipath fault tolerance scheme relies on the existence
and discoverability of multiple redundant paths between the source and
the destination.
Implementation thus requires a routing algorithm.
While not a requirement, this technique is well-suited for
{\em structured networks},
in which links between nodes are constrained to a particular architecture.

In particular, we provide a novel concurrent multipath routing algorithm
on the butterfly network topology and use the partial trust model to prove
a high level of adversarial fault tolerance.
The butterfly topology is popular in parallel processing
\cite{kshemkalyani_distributed_2008} and
peer-to-peer \cite{lua_survey_2005, korzun_structured_2013}
applications, due to its regular structure and high connectivity.
While the ability to control network topology is only achievable in some
applications, those applications are nonetheless significant,
e.g. overlay networks \cite{lua_survey_2005, korzun_structured_2013},
formal organizations \cite{mohr_explaining_1982},
government-regulated cellular networks \cite{walker_mass_2012},
and call tree notification systems \cite{nickerson_thinking_2010}.

Our main contributions are:
\begin{itemize}
\item{We develop a decentralized {\em partial trust model},
which makes weaker transitivity assumptions than web-of-trust models,
and makes it possible to analyze the effect of network structure on
adversarial fault tolerance;}
\item{We show that the partial trust model enables standard fault
tolerance techniques to be applied to adversarial faults in
complex communication networks.
We find that the probability of detecting adversarial faults
approaches 1 exponentially as the number of independent paths between
sender and receiver increases;}
\item{We present a scalable, efficient, and attack-tolerant concurrent
multipath routing algorithm on the butterfly network topology.}
\end{itemize}

This paper is organized as follows.
Section 2. reviews background and related work.
Section 3. discusses the desired properties of attack-tolerant network
infrastructure.
Section 4. describes the partial trust model.
Section 5. describes a general technique for multipath fault tolerance on
structured networks.
Section 6. describes a routing algorithm for multipath fault tolerance
on the butterfly network topology.
Section 7. discusses the our results.
And Section 8. concludes.
